Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-06-17 Supplemental-Material-A-Annotated-Analysis.Rmd
daily and weekly added

# reduced data set for pre measurement
dat.pre.red <- dtS1$raw.pre %>%
  select(-starts_with("t_"))

# merge with daily data [+ clean up]
df.pre <- merge(
  x = dtS1$daily,
  y = dat.pre.red,
  by.x = "last_outside_referrer",
  by.y = "platformId",
  all = T
)

@@

# reduced data set for post-measurement
dat.post.red <- dtS1$raw.post %>%
  select(-starts_with("t_"))

# merge post measurement with pre- and daily data
df <- merge(
  x = df.pre,
  y = dat.post.red,
  by.x = "last_outside_referrer",
  by.y = "last_outside_referrer",
  all = T
)

@@

# create data frame with cleaned data
df <- dtS1$combined %>%
  filter(
    Finished.pre == 1,
    Finished.daily == 1,
    !is.na(last_outside_referrer)
  )

@@

df <- df %>%
  mutate(
    PID = as.numeric(factor(last_outside_referrer)),
    # participant ID
    TID = measureID - 1,
    # time ID with t0 = 0 for meaningfull intercept interpretations
    date = substr(created, 1, 10),
    # awkward way of extracting date (best converted to )
    time = substr(created, 12, 19),
    # awkward way of extracting time
    daynum = as.numeric(factor(dateQualtrics)),
    # all days as numeric for ordering
    daycor = ifelse(
      daytime == "morning" &
        period_to_seconds(hms(time)) < period_to_seconds(hms("12:00:00")) |
        daytime == "afternoon" &
          period_to_seconds(hms(time)) < period_to_seconds(hms("19:00:00")),
      daynum - 1,
      daynum
    ),
    # correctly identify which date the questionnaire is about
    daycor.lead = sprintf("%02d", daycor),
    daytime.lt = ifelse(daytime == "morning", "a", "b"),
    # morning / afternoon to a / b
    day_time = paste(daycor.lead, daytime.lt, sep = "_"),
    # combine day id with morning / afternoon
    ResponseId = as.numeric(factor(day_time)),
    # day and time identifier as numeric id
    SubTime = chron::times(time.0),
    time.daily = as.character(time.daily),
    PPDate = as.Date(df$dateQualtrics.daily),
    number = replace_na(ContactNum, 0),
    NonDutchNum = replace_na(NonDutchNum, 0)
  )

@@

# Prepare dfs for Cleaning
df.pre <- dtS2$raw.pre %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!email %in% .$email[duplicated(.$email)]) %>% # remove all who did the pre questionnaire multiple times (b/c inconsistent ratings scales)
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)

df.post <- dtS2$raw.post %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ResponseId)) %>% # remove own test runs
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  filter(ResponseId %in% df.pre$ResponseId) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  filter(!ResponseId %in% .$ResponseId[duplicated(.$ResponseId)]) %>% # remove all duplicate ResponseIds
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)

@@

# merge daily with pre
dfPreDaily <- merge(
  x = df.daily,
  y = df.pre,
  by = "ResponseId",
  suffixes = c(".daily", ".pre"),
  all = F
)

# merge daily with post
dfCombined <- merge(
  x = dfPreDaily,
  y = df.post,
  by = "ResponseId",
  suffixes = c(".pre", ".post"),
  all = F
)

@@

# Prepare dfs for Cleaning
df.pre <- dtS3$raw.pre %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)

df.post <- dtS3$raw.post %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>% 
  filter(!is.na(ResponseId)) %>% # remove own test runs
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  filter(ResponseId %in% df.pre$ResponseId) %>% # remove anyone who wasn't in the pre
  #filter(!is.na(ended)) %>% # remove all who never finished [disabled because only relevant if data is missing]
  filter(!ResponseId %in% .$ResponseId[duplicated(.$ResponseId)]) %>% # remove all duplicate ResponseIds
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)

@@

# merge daily with pre
dfPreDaily <- merge(
  x = df.daily,
  y = df.pre,
  by = "ResponseId",
  suffixes = c(".daily", ".pre"),
  all = F
)

# merge daily with post
dfCombined <- merge(
  x = dfPreDaily,
  y = df.post,
  by = "ResponseId",
  suffixes = c(".pre", ".post"),
  all = F
)

@@

# Need scales
df$keyMotiveFulfilled <- rowSums(df[, c("KeyNeedFulfillment", "DaytimeNeedFulfillment")], na.rm = T)
df$autonomy.daily.all <- rowSums(df[, c("autonomy", "autonomy_NoInt_1")], na.rm = T)
df$competence.daily.all <- rowSums(df[, c("competence", "competence_NoInt_1")], na.rm = T)
# cor(df$relatednessOther, df$relatedness_self_1,use="complete.obs")
df$relatedness.daily.all <- rowMeans(df[, c(
  "relatednessOther",
  "relatednessSelf",
  "relatednessNoInteraction"
)], na.rm = T)

@@

df$Autonomy <- df$autonomy.daily.all
df$Competence <- df$competence.daily.all
df$Relatedness <- df$relatedness.daily.all

# summarize by participant (check that everything is within pp might not be the case for )
between <- df %>%
  group_by(last_outside_referrer) %>%
  mutate(
    CtContactNL = sum(IntergroupContact),
    CtContactNonNl = sum(IngroupContact),
    CtContactNLAll = sum(ContactNum),
    CtContactNonNlAll = sum(NonDutchNum),
    AvKeyNeed = mean(keyMotiveFulfilled, na.rm = T),
    AvKeyNeedInt = mean(KeyNeedFulfillment, na.rm = T),
    AvKeyNeedNoInt = mean(DaytimeNeedFulfillment, na.rm = T),
    AvAutonomy = mean(autonomy.daily.all, na.rm = T),
    AvCompetence = mean(competence.daily.all, na.rm = T),
    AvRelatedness = mean(relatedness.daily.all, na.rm = T),
    AvThermo = mean(AttitudesDutch, na.rm = T),
    AvWB = mean(exWB, na.rm = T)
  ) %>%
  ungroup() %>%
  mutate(
    CtContactNL_c = scale(CtContactNL, scale = FALSE),
    AvKeyNeedInt_c = scale(AvKeyNeedInt, scale = FALSE),
    AvKeyNeed_c = scale(AvKeyNeed, scale = FALSE),
    CtContactNL_z = scale(CtContactNL, scale = TRUE),
    AvKeyNeedInt_z = scale(AvKeyNeedInt, scale = TRUE),
    AvKeyNeed_z = scale(AvKeyNeed, scale = TRUE)
  )

@@

# Create variables centered and standardized within Participant
# i.e., divide into trait and state
workerWithinBetween <-
  MlTraitState(
    data = workerInteractionType,
    id = "PID",
    selection =
      c(
        "keyMotiveFulfilled",
        "competence.daily.all",
        "autonomy.daily.all",
        "relatedness.daily.all",
        "AttitudesDutch",
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "relatednessNoInteraction", 
        "qualityOverall", 
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )

@@

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("relatednessSelf", "relatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$RelatednessInteraction <- rowMeans(df[c("relatednessSelf", "relatednessOther")], na.rm = TRUE)
df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$Relatedness <-
  rowMeans(df[, c("RelatednessInteraction", "relatednessNoInteraction")],
           na.rm = TRUE) %>%
  ifelse(is.nan(.), NA, .)

@@

# Center within and between
# divide into trait and state
studentWithinBetween <-
  MlTraitState(
    data = studentInteractionType,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "Relatedness",
        "AttitudesDutch",
        "qualityOverall",
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )
studentOutWithinBetween <-
  MlTraitState(
    data = studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "Relatedness",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

@@

# -------------------------------------------------------------------------------------------------------------
#                                 Center Relevant Variables
# -------------------------------------------------------------------------------------------------------------
# divide into trait and state
medicalOutWithinBetween <-
  MlTraitState(
    data = df %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

medicalWithinBetween <-
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall",
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )

df <- # keep only for compatibility of old framgents
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

@@

```{r workerDataAvailability}
dtS1Missing <- dtS1$full %>%
  select(
    PID,
    TIDnum,
    Finished.daily,
    PPDate,
    daytime,
    TID
  ) %>%
  mutate(
    date_period = paste(PPDate, daytime, sep = " "),
    available = 1
  )

dtS1Availability <- dtS1$full %>%
  select(
    PID,
    TIDnum
  ) %>%
  arrange(PID, TIDnum) %>%
  mutate(data = 1)
dtS1Availability <- reshape::cast(dtS1Availability, PID ~ TIDnum) %>%
  select(-PID)
# sum(colMeans(dtS1Availability)*100 >= 66)
# sum(rowMeans(dtS1Availability)*100 >= 66)
# sum(colMeans(dtS1Availability[-5,])*100 >= 66)
# sum(rowMeans(dtS1Availability[,-8])*100 >= 66)

@@

write.csv(dtS1Availability, "data/S1_Workers/processed/workerAvailability.csv")
rm(dtS1Missing)
```

```{r testOptimizer, include=FALSE}
set.seed(42)
df <- as.data.table(matrix(rbinom(10*5,1,.66), ncol=10, nrow=5))
df

@@

```{r studentDataAvailability}
dtS2Missing <- dtS2$full %>%
  select(
    PID,
    date.daily,
    periodMA,
    date_period,
    TID
  ) %>%
  mutate(
    TID = as.numeric(TID),
    available = 1
  )

dtS2Availability <- dtS2$full %>%
  select(
    PID,
    TIDnum
  ) %>%
  arrange(PID, TIDnum) %>%
  mutate(data = 1)
dtS2Availability <- reshape::cast(dtS2Availability, PID ~ TIDnum) %>%
  select(-PID)

@@

write.csv(dtS2Availability, "data/S2_Students/processed/studentAvailability.csv")
rm(dtS2Missing)

@@

```{r medicalDataAvailability}
dtS3Missing <- dtS3$full %>%
  select(
    PID,
    date.daily,
    periodMA,
    date_period,
    TID
  ) %>%
  mutate(
    TID = as.numeric(TID),
    available = 1
  )

dtS3Availability <- dtS3$full %>%
  select(
    PID,
    TIDnum
  ) %>%
  arrange(PID, TIDnum) %>%
  mutate(data = 1)
dtS3Availability <- reshape::cast(dtS3Availability, PID ~ TIDnum) %>%
  select(-PID)

@@

write.csv(dtS3Availability, "data/S3_Medical/processed/medicalAvailability.csv")
rm(dtS3Missing)

@@

@@

```{r workerDataSelection, eval=FALSE}
varListWorker <- 
  c(
    "IntergroupContact",
    "InteractionDum",
    "DaytimeNeedFullfillment",
    "InteractionNeedFullfillment",
    "Autonomy",
    "Competence",
    "Relatedness",
    "AttitudesDutch",
    "AttitudesPartner",
    "ExWB",
    "alertness",
    "calmness",
    "valence",
    "MDMQ.v1_1",
    "MDMQ.v1_2",
    "MDMQ.v1_3",
    "MDMQ.v1_4",
    "MDMQ.v1_5",
    "MDMQ.v1_6",
    "MDMQ.v1_7",
    "MDMQ.v1_8",
    "MDMQ.v1_9",
    "MDMQ.v1_10",
    "MDMQ.v1_11",
    "MDMQ.v1_12",
    "MDMQ.v1_13",
    "MDMQ.v2_1",
    "MDMQ.v2_2",
    "MDMQ.v2_3",
    "MDMQ.v2_4",
    "MDMQ.v2_5",
    "MDMQ.v2_6",
    "MDMQ.v2_7",
    "MDMQ.v2_8",
    "MDMQ.v2_9",
    "MDMQ.v2_10",
    "MDMQ.v2_11",
    "MDMQ.v2_12",
    "MDMQ.v2_13"
  )

>>>>

# reduced data set for pre measurement
dat.pre.red <- dtS1$raw.pre %>%
  select(-starts_with("t_"))
names(dat.pre.red) <- paste(names(dat.pre.red), "pre", sep = ".")

# merge with daily data [+ clean up]
df.pre <- merge(
  x = dtS1$daily,
  y = dat.pre.red,
  by.x = "last_outside_referrer",
  by.y = "platformId.pre",
  all = T
)

@@

# reduced data set for post-measurement
dat.post.red <- dtS1$raw.post %>%
  select(-starts_with("t_"))
names(dat.post.red) <- paste(names(dat.post.red), "post", sep = ".")

# merge post measurement with pre- and daily data
df <- merge(
  x = df.pre,
  y = dat.post.red,
  by.x = "last_outside_referrer",
  by.y = "last_outside_referrer.post",
  all = T
)

@@

# create data frame with cleaned data
df <- dtS1$combined %>%
  filter(
    Finished.pre == 1,
    Finished == 1,
    !is.na(last_outside_referrer)
  )

@@

df <- df %>%
  mutate(
    PID = as.numeric(factor(last_outside_referrer)),
    # participant ID
    TID = measureID - 1,
    # time ID with t0 = 0 for meaningfull intercept interpretations
    date = substr(created, 1, 10),
    # awkward way of extracting date (best converted to )
    time = substr(created, 12, 19),
    # awkward way of extracting time
    daynum = as.numeric(factor(dateQualtrics)),
    # all days as numeric for ordering
    daycor = ifelse(
      daytime == "morning" &
        period_to_seconds(hms(time)) < period_to_seconds(hms("12:00:00")) |
        daytime == "afternoon" &
          period_to_seconds(hms(time)) < period_to_seconds(hms("19:00:00")),
      daynum - 1,
      daynum
    ),
    # correctly identify which date the questionnaire is about
    daycor.lead = sprintf("%02d", daycor),
    daytime.lt = ifelse(daytime == "morning", "a", "b"),
    # morning / afternoon to a / b
    day_time = paste(daycor.lead, daytime.lt, sep = "_"),
    # combine day id with morning / afternoon
    ResponseId = as.numeric(factor(day_time)),
    # day and time identifier as numeric id
    SubTime = chron::times(time.0),
    time.daily = as.character(time),
    PPDate = as.Date(df$dateQualtrics),
    number = replace_na(ContactNum, 0),
    NonDutchNum = replace_na(NonDutchNum, 0)
  )

@@

# Prepare dfs for Cleaning
df.pre <- dtS2$raw.pre %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!email %in% .$email[duplicated(.$email)]) %>% # remove all who did the pre questionnaire multiple times (b/c inconsistent ratings scales)
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)
names(df.pre) <- paste(names(df.pre), "pre", sep = ".")

df.post <- dtS2$raw.post %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ResponseId)) %>% # remove own test runs
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  filter(ResponseId %in% df.pre$ResponseId) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  filter(!ResponseId %in% .$ResponseId[duplicated(.$ResponseId)]) %>% # remove all duplicate ResponseIds
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)
names(df.post) <- paste(names(df.post), "post", sep = ".")

@@

# merge daily with pre
dfPreDaily <- merge(
  x = df.daily,
  y = df.pre,
  by.x = "ResponseId",
  by.y = "ResponseId.pre", 
  suffixes = c(".daily", ".pre"),
  all = FALSE
)

# merge daily with post
dfCombined <- merge(
  x = dfPreDaily,
  y = df.post,
  by.x = "ResponseId",
  by.y = "ResponseId.post", 
  suffixes = c(".pre", ".post"),
  all = FALSE
)

@@

# Prepare dfs for Cleaning
df.pre <- dtS3$raw.pre %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)
names(df.pre) <- paste(names(df.pre), "pre", sep = ".")

df.post <- dtS3$raw.post %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>% 
  filter(!is.na(ResponseId)) %>% # remove own test runs
  filter(!ResponseId %in% ownIDs) %>% # remove our own test
  filter(ResponseId %in% df.pre$ResponseId) %>% # remove anyone who wasn't in the pre
  #filter(!is.na(ended)) %>% # remove all who never finished [disabled because only relevant if data is missing]
  filter(!ResponseId %in% .$ResponseId[duplicated(.$ResponseId)]) %>% # remove all duplicate ResponseIds
  mutate(ResponseId = as.character(ResponseId)) # turn factor into character strings (probably just precaution)
names(df.post) <- paste(names(df.post), "post", sep = ".")

@@

# merge daily with pre
dfPreDaily <- merge(
  x = df.daily,
  y = df.pre,
  by.x = "ResponseId",
  by.y = "ResponseId.pre", 
  suffixes = c(".daily", ".pre"),
  all = F
)

# merge daily with post
dfCombined <- merge(
  x = dfPreDaily,
  y = df.post,
  by.x = "ResponseId",
  by.y = "ResponseId.post", 
  suffixes = c(".pre", ".post"),
  all = F
)

@@

# Need scales
df$keyMotiveFulfilled <- rowSums(df[, c("KeyNeedFulfillment", "DaytimeNeedFulfillment")], na.rm = T)
df$autonomy.daily.all <- rowSums(df[, c("autonomy_Int", "autonomy_NoInt")], na.rm = T)
df$competence.daily.all <- rowSums(df[, c("competence_Int", "competence_NoInt")], na.rm = T)
# cor(df$relatednessOther, df$relatedness_self_1,use="complete.obs")
df$relatedness.daily.all <- rowMeans(df[, c(
  "relatednessOther",
  "relatednessSelf",
  "relatednessNoInteraction"
)], na.rm = T)

@@

df$autonomy <- df$autonomy.daily.all
df$competence <- df$competence.daily.all
df$relatedness <- df$relatedness.daily.all

# summarize by participant (check that everything is within pp might not be the case for )
between <- df %>%
  group_by(last_outside_referrer) %>%
  mutate(
    CtContactNL = sum(IntergroupContact),
    CtContactNonNl = sum(IngroupContact),
    CtContactNLAll = sum(ContactNum),
    CtContactNonNlAll = sum(NonDutchNum),
    AvKeyNeed = mean(keyMotiveFulfilled, na.rm = T),
    AvKeyNeedInt = mean(KeyNeedFulfillment, na.rm = T),
    AvKeyNeedNoInt = mean(DaytimeNeedFulfillment, na.rm = T),
    AvAutonomy = mean(autonomy, na.rm = T),
    AvCompetence = mean(competence, na.rm = T),
    AvRelatedness = mean(relatedness, na.rm = T),
    AvThermo = mean(AttitudesDutch, na.rm = T),
    AvWB = mean(exWB, na.rm = T)
  ) %>%
  ungroup() %>%
  mutate(
    CtContactNL_c = scale(CtContactNL, scale = FALSE),
    AvKeyNeedInt_c = scale(AvKeyNeedInt, scale = FALSE),
    AvKeyNeed_c = scale(AvKeyNeed, scale = FALSE),
    CtContactNL_z = scale(CtContactNL, scale = TRUE),
    AvKeyNeedInt_z = scale(AvKeyNeedInt, scale = TRUE),
    AvKeyNeed_z = scale(AvKeyNeed, scale = TRUE)
  )

@@

# Create variables centered and standardized within Participant
# i.e., divide into trait and state
workerWithinBetween <-
  MlTraitState(
    data = workerInteractionType,
    id = "PID",
    selection =
      c(
        "keyMotiveFulfilled",
        "competence",
        "autonomy",
        "relatedness",
        "AttitudesDutch",
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "relatednessNoInteraction", 
        "qualityOverall", 
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )

@@

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("relatednessSelf", "relatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$relatednessInteraction <- rowMeans(df[c("relatednessSelf", "relatednessOther")], na.rm = TRUE)
df$relatednessInteraction[df$relatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$relatedness <-
  rowMeans(df[, c("relatednessInteraction", "relatednessNoInteraction")],
           na.rm = TRUE) %>%
  ifelse(is.nan(.), NA, .)

@@

# Center within and between
# divide into trait and state
studentWithinBetween <-
  MlTraitState(
    data = studentInteractionType,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "relatedness",
        "AttitudesDutch",
        "qualityOverall",
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )
studentOutWithinBetween <-
  MlTraitState(
    data = studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "relatedness",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

@@

# -------------------------------------------------------------------------------------------------------------
#                                 Center Relevant Variables
# -------------------------------------------------------------------------------------------------------------
# divide into trait and state
medicalOutWithinBetween <-
  MlTraitState(
    data = df %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

medicalWithinBetween <-
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall",
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )

df <- # keep only for compatibility of old framgents
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "competence",
        "autonomy",
        "relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

@@

```{r workerDataAvailability}
dtS1Availability <- dtS1$full %>%
  select(
    PID,
    TIDnum
  ) %>%
  arrange(PID, TIDnum) %>%
  mutate(data = 1)
dtS1Availability <- reshape::cast(dtS1Availability, PID ~ TIDnum) %>%
  select(-PID) %>%
  mutate_all(function(x) ifelse(x>1,1,x))
# sum(colMeans(dtS1Availability)*100 >= 66)
# sum(rowMeans(dtS1Availability)*100 >= 66)
# sum(colMeans(dtS1Availability[-5,])*100 >= 66)
# sum(rowMeans(dtS1Availability[,-8])*100 >= 66)

@@

write.csv(dtS1Availability, "data/S1_Workers/processed/workerAvailability.csv")
```

```{r testOptimizer, include=FALSE}
set.seed(42)
df <- as.data.table(matrix(rbinom(5*10,1,.66), nrow=5, ncol=10))
df

@@

```{r studentDataAvailability}
dtS2Availability <- dtS2$full %>%
  select(
    PID,
    TIDnum
  ) %>%
  arrange(PID, TIDnum) %>%
  mutate(data = 1)
dtS2Availability <- reshape::cast(dtS2Availability, PID ~ TIDnum) %>%
  select(-PID)

@@

write.csv(dtS2Availability, "data/S2_Students/processed/studentAvailability.csv")

@@

```{r medicalDataAvailability}
dtS3Availability <- dtS3$full %>%
  select(
    PID,
    TIDnum
  ) %>%
  arrange(PID, TIDnum) %>%
  mutate(data = 1)
dtS3Availability <- reshape::cast(dtS3Availability, PID ~ TIDnum) %>%
  select(-PID)

@@

write.csv(dtS3Availability, "data/S3_Medical/processed/medicalAvailability.csv")

@@

```{r checkVarAvailability}
varNamesPre <- varNames %>%
  filter(
    surveyS1 == "pre",
    surveyS2 == "pre",
    str_detect(surveyS3, "^pre")
  ) %>%
  select(varNam)
varNamesPreFull <-
  data.frame(varNam = Reduce(intersect, list(
    names(dtS1$full), names(dtS3$full), names(dtS3$full)
  ))) %>%
  filter(str_detect(varNam, ".pre$"))

varNamesDaily <- varNames %>%
  filter(
    surveyS1 == "daily",
    surveyS2 == "daily",
    surveyS3 == "daily"
  ) %>%
  select(varNam)
varNamesDailyFull <-
  data.frame(varNam = Reduce(intersect, list(
    names(dtS1$full), names(dtS3$full), names(dtS3$full)
  ))) %>%
  filter(!str_detect(varNam, ".pre$|.post$"))

varNamesPost <- varNames %>%
  filter(
    surveyS1 == "post",
    surveyS2 == "post",
    surveyS3 == "post"
  ) %>%
  select(varNam)
varNamesPostFull <-
  data.frame(varNam = Reduce(intersect, list(
    names(dtS1$full), names(dtS3$full), names(dtS3$full)
  ))) %>%
  filter(str_detect(varNam, ".post$"))
```

```{r analysisDFs}
# Main Analysis: 3MPCA (common variables across studies)
dropVarPcaMain <- c(
  # Meta Data
  "last_outside_referrer",
  "created",
  "ended",
  "ip_address",
  "date",
  "ResponseId",
  "server_language",
  "Meta_Browser",
  # Interaction Dummies (non-continuous)
  "IntergroupContact",
  "IngroupContact",
  "InteractionDum",
  # Interaction Counts (non-continuous)
  "ContactNum",
  "NonDutchNum",
  # Interaction Descriptives (non-continuous)
  "duration",
  "dyadGroup",
  "groupSize",
  # Keyneed Freetexts (non-continuous)
  "KeyNeed",
  "DaytimeNeed",
  # Relatedness individual items
  "relatednessSelf",
  "relatednessOther",
  "relatednessNoInteraction"
)

varNam3mpcaMain <- varNamesDailyFull %>%
  filter(!varNam %in% dropVarPcaMain) %>%
  pull

dtMain3mpca <- rbind(
  dtS1$full %>% select(any_of(varNam3mpcaMain)) %>% mutate(study = "S1"),
  dtS3$full %>% select(any_of(varNam3mpcaMain)) %>% mutate(study = "S2"),
  dtS3$full %>% select(any_of(varNam3mpcaMain)) %>% mutate(study = "S3")
  ) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
    ) %>%
  select(
    ID,
    PID,
    TID,
    date,
    week,
    TIDnum,
    study,
    everything()
  ) %>%
  arrange(ID, TIDnum)

dtMain3mpcaDaily <- dtMain3mpca %>%
  group_by(ID, date, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(date))) %>%
  ungroup %>%
  select(ID, date, TIDnum, everything()) %>%
  mutate_all(~ifelse(is.nan(.), NA, .))

dtMain3mpcaWeekly <- dtMain3mpca %>%
  group_by(ID, week, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(week))) %>%
  ungroup %>%
  select(ID, week, TIDnum, everything()) %>%
  mutate_all(~ifelse(is.nan(.), NA, .))

dtMain3mpcaWeekly

stats::reshape(dtMain3mpca, idvar = "ID", timevar = "TIDnum", direction = "wide")

@@

```{r workerDataSelection, eval=FALSE}
varListWorker <- 
  c(
    "IntergroupContact",
    "InteractionDum",
    "DaytimeNeedFullfillment",
    "InteractionNeedFullfillment",
    "autonomy",
    "competence",
    "relatedness",
    "AttitudesDutch",
    "AttitudesPartner",
    "ExWB",
    "alertness",
    "calmness",
    "valence",
    "MDMQ.v1_1",
    "MDMQ.v1_2",
    "MDMQ.v1_3",
    "MDMQ.v1_4",
    "MDMQ.v1_5",
    "MDMQ.v1_6",
    "MDMQ.v1_7",
    "MDMQ.v1_8",
    "MDMQ.v1_9",
    "MDMQ.v1_10",
    "MDMQ.v1_11",
    "MDMQ.v1_12",
    "MDMQ.v1_13",
    "MDMQ.v2_1",
    "MDMQ.v2_2",
    "MDMQ.v2_3",
    "MDMQ.v2_4",
    "MDMQ.v2_5",
    "MDMQ.v2_6",
    "MDMQ.v2_7",
    "MDMQ.v2_8",
    "MDMQ.v2_9",
    "MDMQ.v2_10",
    "MDMQ.v2_11",
    "MDMQ.v2_12",
    "MDMQ.v2_13"
  )

varNameListWorker <- 
  c(
    "IntergroupContact" = "Dutch Interaction",
    "InteractionDum" = "Any Interaction",
    "DaytimeNeedFullfillment" = "Daytime Core Motive Fulfillment",
    "InteractionNeedFullfillment" = "Interaction Core Motive Fulfillment",
    "autonomy" = "Autonomy",
    "competence" = "Competence",
    "relatedness" = "Relatedness",
    "AttitudesDutch" = "Outgroup Attitude",
    "AttitudesPartner" = "Attitude Interaction Partner",
    "ExWB" = "Sadness Happiness",
    "alertness" = "Alertness",
    "calmness" = "Calmness",
    "valence" = "Emotional Valence",
    "MDMQ.v1_1" = "content",
    "MDMQ.v1_2" = "rested",
    "MDMQ.v1_3" = "restless",
    "MDMQ.v1_4" = "bad",
    "MDMQ.v1_5" = "worn-out",
    "MDMQ.v1_6" = "composed",
    "MDMQ.v1_7" = "tired",
    "MDMQ.v1_8" = "great",
    "MDMQ.v1_9" = "uneasy",
    "MDMQ.v1_10" = "energetic",
    "MDMQ.v1_11" = "uncomfortable",
    "MDMQ.v1_12" = "relaxed",
    "MDMQ.v1_13" = "alive and vital",
    "MDMQ.v2_1" = "sleepy",
    "MDMQ.v2_2" = "good",
    "MDMQ.v2_3" = "at ease",
    "MDMQ.v2_4" = "unhappy",
    "MDMQ.v2_5" = "alert",
    "MDMQ.v2_6" = "discontent",
    "MDMQ.v2_7" = "tense",
    "MDMQ.v2_8" = "fresh",
    "MDMQ.v2_9" = "happy",
    "MDMQ.v2_10" = "nervous",
    "MDMQ.v2_11" = "exhausted",
    "MDMQ.v2_12" = "calm",
    "MDMQ.v2_13" = "alive and vital"
  )
